---
title: "RENEW Data Report"
author: "Magali Blanco"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---


**To do:**   

* quizzes   
    + analyze pn_training w/ and w/o sup   

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, cache=T, cache.comments = F, message = F, warning = F, tidy.opts=list(width.cutoff=60), tidy=TRUE, fig.height = 8)  

# Clear workspace of all objects and unload all extra (non-base) packages
rm(list = ls(all = TRUE))
if (!is.null(sessionInfo()$otherPkgs)) {
  res <- suppressWarnings(
    lapply(paste('package:', names(sessionInfo()$otherPkgs), sep=""),
      detach, character.only=TRUE, unload=TRUE, force=TRUE))
}

pacman::p_load(readxl, table1, tidyverse, knitr, kableExtra)

source("Var&Fns.R")

######################################### Load data #########################################

pn_dem <- read_excel("Data/peer navigator initial questionnaires.xlsx")
pn_train_eval <- read_excel("Data/peer navigator training evaluations.xlsx")
pn_quiz <- read_excel("Data/peer navigator training quizzes.xlsx")

#attach(pn_quiz)
pn_quiz <- pn_quiz %>%
  mutate(
    #recode supervisor
    id = recode(id, Supervisor = "999")) %>%
  #convert character columns to numbers 
  mutate_if(is.character, as.numeric) %>%
  #drop individuals who only completed 1 survey
  filter(!id %in% c(2, 3))

```


# Peer Navigators 

```{r}
### --> ?? no "English as primary langugae" Q. get from benefits group?

```

## Demographics   
From initial Questionnaires 

```{r}
######################################### Demographics #########################################
#Table 1 for peer navigators
pn_dem %>%
  t1.fn(column.name = "Peer Navigators") %>%
  filter(substr(x = get("Peer Navigators"), 1,1) != "0") %>%
  kable(caption = "Participant Demographics & Work Characteristics", 
        #format = "latex"
        ) %>%
  pack_rows("Race", 4, 7,  bold = F, label_row_css = F) %>%
  pack_rows("Education", 9, 11, label_row_css = F,  bold = F) %>%
  #work around since bold=F doesn't work in pack_rows()  
  gsub(pattern = "(<strong>)|<strong/>", replacement = "")
 
```

## Chronic Pain (n, %)

```{r}
######################################### Chronic Pain #########################################

pn_pain_known = sum(!is.na(pn_dem$chronic_pain))
pn_pain_yes_n = sum(pn_dem$chronic_pain == 1, na.rm = T)
pn_pain_yes_pct = paste0(mean(pn_dem$chronic_pain, na.rm = T)*100)

pn_pain_n_pct <- paste0(pn_pain_yes_n, " (", pn_pain_yes_pct, "%)") 

pn_pain_n_pct %>%
  kable(col.names = "Peer Navigators", 
        caption = "History of chronic musculoskeletal pain")

```

# Training evaluations

Excludes:   

* open ended responses    

```{r}
######################################### Training Evaluations #########################################
# w/o supervisor
pn_train_eval %>%
  #drop supervisor & 2 PNs that didn't complete survey 
  filter(id != "supervisor") %>%
  training.eval.fn() %>%
  kable(caption = "Peer Navigators Training and Program Feedback. Number (%) of individuals who 'Agree' or 'Strongly Agree'. Excludes supervisor.",  
        col.names = c("Measure", "1", "2"),  
        ) %>%
  add_header_above(c(" " = 1, "Training" = 2))  
 #cat(., file = "df.html") 
   
# w/ supervisor
pn_train_eval %>%
  #drop supervisor & 2 PNs that didn't complete survey 
  training.eval.fn() %>%
  kable(caption = "Peer Navigators Training and Program Feedback. Number (%) of individuals who 'Agree' or 'Strongly Agree'. Includes supervisor.",  
        col.names = c("Measure", "1", "2"),  
        ) %>%
  add_header_above(c(" " = 1, "Training" = 2))  
  
```

## Quizzes

```{r}
######################################### Quizzes #########################################

max_score <- 16

pn_quiz <- pn_quiz %>%
  #drop supervisor
  filter(id != 999) %>%
  #label correct answers based on whether individuals received full credit
  mutate(
    wc_benefits_cor = as.numeric(wc_benefits == 5),
    wc_medical_coverage_cor = as.numeric(wc_medical_coverage == 1),
    on_job_injuries_cor = as.numeric(on_job_injuries == 4),
    smoking_cor = as.numeric(smoking == 1),
    wc_provider_cor = as.numeric(wc_provider==1),
    second_opinion_cor = as.numeric(second_opinion == 4)) 

quiz_scores <- pn_quiz %>%
  select(id, training, total_score:second_opinion_cor) %>%
  group_by(training) %>%
  summarize(
    tot_score = round(mean(total_score/max_score)*100),
    wc_benefits = round(mean(wc_benefits_cor)*100),
    wc_medical_coverage = round(mean(wc_medical_coverage_cor)*100),
    on_job_injuries = round(mean(on_job_injuries_cor)*100),
    smoking = round(mean(smoking_cor)*100),
    wc_provider = round(mean(wc_provider_cor)*100),
    second_opinion = round(mean(second_opinion_cor)*100)) 

quiz_scores <- t(quiz_scores) %>%
  #paste0(., "%")
    as.data.frame() %>%
    rownames_to_column()

names(quiz_scores) <- c("Allias", "Pre", "Post1", "Post2")

quiz_scores <- quiz_scores %>%
  slice(-1) %>%
  mutate(
    Question = c("Mean total quiz score",
              "What kind of benefits does WC cover? (multiple choice)",
              "A caregiver will only get medical coverage through WC if their injury requires them to take time off of work",
              "Which are on-the-job injuries? (multiple choice)",
              "Stopping smoking can help caregivers recover after they are injured on the job",
              "The attending provider is the only provider covd under the WC claim",
              "Reasons for wanting to get a second opinion (multiple choice)"
              ),
    Pre = paste0(Pre, "%"),
    Post1 = paste0(Post1, "%"),
    Post2 = paste0(Post2, "%"),
    )

quiz_scores %>%
  select(Allias, Question, Pre:Post2) %>%
  kable(caption = paste0("Quiz scores before (Pre) and after (Post 1, Post 2) each training module. Percent of individuals who answered correctly. N = ", length(unique(pn_quiz$id)), ".")) %>%
  add_header_above(c(" " = 2, "Training" = 3))

```

```{r, eval=T}

quiz_scores.l <- quiz_scores %>%
  gather("Training", "Correct", Pre:Post2) %>%
  mutate(
    Training = factor(Training, levels = c("Pre", "Post1", "Post2")),
    Correct = as.numeric(substr(Correct, 1,  nchar(Correct)-1))/100,
    Allias = relevel(as.factor(Allias), ref = "tot_score")
         ) 

quiz_scores.l %>%
  ggplot(aes(x=Allias, y=Correct, fill=Training)) + 
  geom_bar(position = "dodge", stat = "identity") + 
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) + 
  scale_y_continuous(labels = scales::percent) #+ 
  #labs(title = "Quiz scores before (Pre) and after (Post 1, Post 2) each training module.\nPercent of individuals who answered correctly.")

```

T-test comparing Pre-training vs Training 2 total quiz scores

```{r}

#reorganize total training scores
quiz_tot_scores <- pn_quiz %>%
  select(id, training, total_score) %>%
  spread(training, total_score, sep = "_")

(quiz_t_test <- t.test(x=quiz_tot_scores$training_0, 
       y= quiz_tot_scores$training_2))


quiz_t_p <- ifelse(round(quiz_t_test$p.value, 3) > 0.001, 
       round(quiz_t_test$p.value, 3), 
       "< 0.001")

#paste0("t-test p-val comparing pre-training to training 2 total quiz scores: ", quiz_t_p)

```

Wilcoxon Signed-Rank test. A non-parametric (paired) test or whether two distributions are identical without assuming them to be normally distributed. 

```{r}
(quiz_wilcox_test <- wilcox.test(x=quiz_tot_scores$training_0, 
       y= quiz_tot_scores$training_2, 
       paired = TRUE, 
       alternative = "two.sided")
)

quiz_wilcox_p <- ifelse(round(quiz_wilcox_test$p.value, 3) > 0.001, 
       round(quiz_wilcox_test$p.value, 3), 
       "< 0.001")


```



\newpage
```{r}
# HCAs
```




\newpage
# Code

```{r,ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60), include=T}
```

